Best Practices for Alchemical Free Energy Calculations: v\versionnumber

### 2019-12-11 paper/manuscript.tex
fixing wrong relative file paths

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% IMPORTANT USER CONFIGURATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[most]{tcolorbox}
\usepackage{enumitem,amssymb}
\usepackage{textgreek}
\usepackage{changepage}

\newcommand{\versionnumber}{0.1}  % you should update the minor version number in preprints and major version number of submissions.
\newcommand{\githubrepository}{\url{https://github.com/michellab/alchemical-best-practices}}  %this should be the main github repository for this article
\newcommand{\expect}[1]{\left\langle{#1}\right\rangle}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% ARTICLE SETUP
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Best Practices for Alchemical Free Energy Calculations: v\versionnumber}
\author[7]{Bryce K. Allen}
\author[1*]{John D. Chodera}
\author[2,12]{Maximilian Kuhn}
\author[2*]{Antonia S. J. S. Mey}
\author[2*]{Julien Michel}
\author[3*]{David L. Mobley}
\author[1]{Levi N. Naden}
\author[4]{Samarjeet Prasad}
\author[5]{Julia E. Rice}
\author[1,9]{Andrea Rizzi}
\author[2]{Jenke Scheen}
\author[6*]{Michael Shirts}
\author[11]{Gary Tresadern}
\author[10]{Huafeng Xu}

@@

\begin{figure}
    \includegraphics[width=0.95\linewidth]{paper/figures/fig1_what_is_alchemy/Fig1.pdf}    \caption{Illustration of the types of free energies differences that can be calculated using alchemical free energy methods. A: Change in free energy due to a conformational change. B: Partition coefficient such as $\log P$ or $\log D$, here as an example the partition coefficient between methanol and water of a given molecule. C: Free energies of membrane insertions. D: Simulations of protein or other host molecule simulations. E: Absolute free energies of binding of a small molecule to a host (e.g. protein), F: Relative free energy of binding of one molecule with respect to another, here toluene and benzyl alcohol.
    \label{fig:fig1_what_is_alchemy}
    }
\end{figure}

@@

    \includegraphics[width=0.95\linewidth]{paper/figures/fig2_what_is_lam/Fig2.pdf}

@@

\begin{figure}
    \includegraphics[width=0.95\linewidth]{paper/figures/fig3_therm_cyc/Fig3.pdf}
    \caption{{\bf Thermodynamic cycle for computing the relative free energy of binding ($\Delta \Delta G$) between two related small molecules to a supramolecular host.}
    The relative binding free energy difference between two small molecules, $\Delta \Delta G_{\mathrm{bind}, A \rightarrow B} \equiv \Delta G_{\mathrm{bind}, B} - \Delta G_{\mathrm{bind}, A}$---here benzyl alcohol (top) to toluene (bottom)---can be computed as a difference between two alchemical transformations, $\Delta G_\mathrm{bound} - \Delta G_\mathrm{solvated}$, where $\Delta G_\mathrm{bound}$ represents the free energy change of transforming $A \rightarrow B$ in complex and $\Delta G_\mathrm{solvated}$ the free energy change of transforming $A \rightarrow B$ in solvent.}
    \label{fig:fig3_binding-thermodynamic-cycle}
\end{figure}
\todo[inline, color=green!20]{This section needs to be expanded and give a good introduction to the theoretical background without going into too much detail.}

@@

Running binding FE calculations in a drug discovery application will typically require the use of software or tools to facilitate the calculations of many compounds. The commercial implementation from Schrodinger, FEP+, uses a graphical user interface and once the user has calculated any missing force field parameters, calculations can be prepared and submitted within minutes. The software builds the network of perturbations, connecting similar compounds based on LOMAP methodology~\cite{liu2013lead}, all inputs for the Desmond simulations are built automatically and the job can be saved or run immediately on available GPUs. The cost of this software is often prohibitive but alternative tools are becoming available to allow relatively straight forward running of alchemical FE calculations with other software~\cite{gapsys2015pmx, loeffler2015fesetup} (CITE New Merz paper, cite PMX paper Vytas and Bert de Groot, cite FESETUP, cite FEanalysis). One consideration at this point is to define the perturbations suitable for the application. For instance, if the goal is to accurately assess the relative binding energy of a small number of compounds, possibly with challenging synthesis, the map of perturbations may contain as many connections between compounds as affordable. However, when running calculations on hundreds of compounds a so called ‘star-map’ can be used that just contains one connection per compound: perturbing every compound to a central ligand, typically the crystal structure ligand. In this way the top-ranking examples can be readily identified and submitted to additional calculations in a second round. 

@@

\paragraph{Topologies} A critical first step in relative calculations is to select an approach to these calculations, determining whether to use a \emph{dual topology}, \emph{single topology}, or \emph{hybrid topology} approach to relative calculations.
\begin{figure}
    \includegraphics[width=0.95\columnwidth]{paper/figures/fig4_topol/Fig4.pdf}
    \caption{top: single topology bottom: dual topology Figure adapted from \url{http://www.alchemistry.org/wiki/Constructing_a_Pathway_of_Intermediate_States}}
    \label{fig:fig4_topology}
\end{figure} 
The distinction between these can be illustrated by considering a hypothetical transformation from molecule A to molecule B, where both atoms share a common substructure but differ in which functional groups are present; e.g. consider a transformation of benzene (A) to benzyl alcohol (B)~\ref{fig:fig4_topology}.
In this case the common substructure is the benzene ring, though perhaps may be larger depending on how it is defined, as we discuss below.
In single topology calculations, the overall transformation is set up to involve as few additional atoms as possible, so benzene would be typically changed into benzyl alcohol by changing one of the hydrogens into a carbon. To this new carbon you also find non-interacting atoms called ``dummy atoms'' (retaining their bonded interactions but not interacting with the rest of the system), which will become the two hydrogens attached to the new carbon and the OH group. Bond parameters as well as partial charges are adjusted accordingly. 
Thus in a single topology calculation, atoms may change their type so relatively few dummy atoms are created. This is illustrated in fig.~\ref{fig:fig4_topology} (a). 
In contrast, in a dual topology free energy calculation, no atoms are allowed to change type~\cite{shirts2012best}. This means that the benzene to benzyl alcohol transformation involves starting with benzene plus the non-interacting dummy atoms making up the hydroxy methyl group, then passing through an intermediate state where atoms which are becoming dummy atoms or ceasing being dummy atoms are partially interacting (this state may or may not be well defined~\cite{mobley2014blind}  and culminating in a state where benzyl alcohol is present along with the additional dummy atoms which was previously a corresponding hydrogen of the benzene. Fig.~\ref{fig:fig4_topology} (b) depicts how such a dual topology works.

@@

\paragraph{Atom mapping}
Once a particular approach to the topology is selected, a crucial next step is to identify the common atoms which will not be perturbed.
Rigorously, this process essentially comprises a maximal common substructure (MCSS) search of the molecules involved to identify the common substructure -- though the parameters of the MCSS search will differ depending on whether single or dual topology calculations are planned.
Specifically, with a single topology approach in mind, atom types are allowed to change, so a permissive MCSS search can be done, whereas with dual topology a more strict search is required.
\begin{figure}
    \includegraphics[width=0.95\linewidth]{paper/figures/fig5_mcs/MCS.pdf}
    \caption{A: restrictive MCSS match B: ring breaking}
    \label{fig:fig5_mcss}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=0.95\linewidth]{paper/figures/fig6_thermo_cyc_abs/fig6_therm_abs.pdf}
    \caption{Absolute thermodynamic cycle}
    \label{fig:fig6_absolute-thermodynamic-cycle}
\end{figure}

@@

\ref{fig:fig7_ampling_scheme} A:\cite{hedges2019biosimspace, song2019using } B\cite{aldeghi2015accurate, wang2015accurate,jiang2019computing} C:\cite{li2007simulated, tan2017optimally} D:\cite{aldeghi2018accurate}
\begin{figure}
    \includegraphics[width=0.95\columnwidth]{paper/figures/fig7_sampl_scheme/sampling_schemes.pdf}
    \caption{\textbf{There are 4 different sampling strategies available and implementations are available for different software packages.} A: Multiple replicas in parallel at different lambda states. B: Hamiltonian replica exchange scheme. C: Single replica scheme sampling from all $\lambda$ states. D: Non-equilibrium sampling scheme.}
    \label{fig:fig7_sampling_scheme}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.95\linewidth]{paper/figures/fig9_forward_reverse/Forward_Reverse_Fig.pdf}
    \caption{Free energy (in k$_{B}$T) for two different relative binding free energy (RBFE) perturbations. 
    Each plot shows the estimated free energy change using a varying fraction of total simulation time (up to 5 ns total). 
    The top panel shows the three-step protocol for a perturbation involving 5 perturbed atoms, while the bottom panel shows the same protocol for a perturbation involving 10 perturbed atoms. The difference in energy between the forward (blue) and reverse (red) free energy calculations at the midpoint of the simulation time gives an indication of the overall convergence of the simulation, with differences over 1 k$_{B}$T indicating poor convergence.}
    \label{fig:convergence_forward_reverse}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.95\linewidth]{paper/figures/fig10_equib_detection/fig10_equib.pdf}
    \caption{{\bf Automatic partitioning into equilibration and production regions.}
    \emph{Top:} The average (black line) standard deviation (shaded region) of the reduced potential $u^*$ over many independent replicate simulations started from the same initial conditions show a significant initial transient before relaxing to the true average potential energy.
    \emph{Middle:} A cumulative average (red) of the entire simulation data demonstrates a bias in the estimate of the average potential $<u>$ that persists far beyond the initial transient relaxation time, while averaging a production region that omits the initial transient (blue) eliminates this bias.
    \emph{Bottom:} A simple automated approach to determination of the equilibration boundary $t_0$ suggested in~\cite{chodera2016simple} examines the number of effectively uncorrelated samples $N_{\mathrm{eff}_{[t_0,T]}} = (T-t_0) / g_{[t_0,T]}$ within the proposed production region $[t_0,T]$ by computing the statistical inefficiency $g_{[t_0,T]}$ for that simulation interval.
    $N_{\mathrm{eff}_{[t_0,T]}}$ has the general behavior of increasing linearly as $t_0$ moves backwards from $T$ until the initial transient relaxation is encountered, at which point it plunges.
    The optimal equilibration boundary $t_0$ is selected to maximize the number of uncorrelated samples.
    \emph{Figure adapted from~\cite{chodera2016simple}.}
    \todo[inline]{JDC will update this figure with something similar for a real alchemical free energy calculation.}
    }
    \label{fig:automatic-equilibration-detection}
\end{figure}

@@

\includegraphics[width=0.95\columnwidth]{paper/figures/fig11_overlap/overlap_matrices.pdf}

@@

\todo[inline, color={green!20}]{ASJSM: Please upload the correct figure here and modify the path below}
\begin{figure}
    \includegraphics[width=0.95\linewidth]{paper/figures/fig8_convergence/free_energy_trajectories.pdf}
    \caption{Average binding free energy of 5 replicate Hamiltonian replica exchange calculations as a function of total simulation time (i.e. the sum of the simulation time of all replicas) for the two host-guest systems CB8-G3 and OA-G3. Shaded areas represent 95\% confidence intervals around the mean computed from the 5 replicates data. The horizontal dashed lines show the final binding free energy prediction of the two calculations after a total of ~5230 ns for OA-G3 and ~6650 ns for CB8-G3. Longer correlation times in CB8-G3 cause the calculation to converge more slowly. The original data used to generate the plot can be found at \url{https://github.com/MobleyLab/SAMPL6/blob/master/host_guest/Analysis/SAMPLing/Data/reference_free_energies.csv}.
}
    \label{fig:freeenergytrajectories}
\end{figure}

@@

\section{Checklist}
\label{sec:checklist}
\todo[inline, color={green!20}]{JS: @everyone Please input your own suggestions, I made some points off the top of my head. Feel free to add helpful citations to any of the bullet points}
\todo[inline, color={green!20}]{JS: @self,ASJSM do some final formatting when text is complete.}

% This provides a checklist which
% - spans a full page
% - consists of multiple sub-checklists
% - exists on a separate page
% This style of checklist will be especially helpful if you want to encourage readers to print and use your checklist in practice, as they
% can easily print it without also printing other material from your manuscript. However, other styles of checklist are also possible (below).
% \begin{Checklists*}[p!]

% \begin{checklist}{Step 0 -- Know what you want to simulate }
% \textbf{What are the first questions that need addressing before setting up a molecular dynamics simulation}\\
% Extensive explanation for the checklist questions can be found in Section~\ref{sec:step0}.
% \begin{itemize}
% \item Can I get the required accuracy with the simulation I want to carry out?
% \item Have I properly prepared my protein and ligand systems?
% \item Does my system contain any groups that require custom parameters?
% \item What simulation protocol will provide the most evidence to answer my hypothesis?

% \item And finally
% \end{itemize}
% \end{checklist}

% \begin{checklist}{Simulation preparation}
% \textbf{How do I get started setting up an alchemical free energy calculation}
% Extensive explanation for the checklist questions can be found in Section~\ref{sec:step1}.
% \begin{itemize}
% \item Have I followed the Best practices for biomolecular simulation set up?
% \item In a relative simulation, will I run into problems with clashing geometries in the ligand transformation or crystal waters?
% \end{itemize}
% \end{checklist}
% \end{Checklists*}

% \begin{Checklists*}[p!]
% \begin{checklist}{Absolute simulations}
% \textbf{What are the main things I need to consider for an absolute alchemical free energy calculation?}
% Extensive explanation for the checklist questions can be found in Section~\ref{sec:step2}.
% \begin{itemize}
% \item Topology
% \item Restraints
% \item Standard state handling
% \end{itemize}
% \end{checklist}

% \begin{checklist}{Relative simulations}
% \textbf{What are the main things I need to consider for an relative alchemical free energy calculation?}
% Extensive explanation for the checklist questions can be found in Section~\ref{sec:step2}.
% \begin{itemize}
% \item First thing
% \item Also remember
% \item And finally
% \end{itemize}
% \end{checklist}

% \begin{checklist}{Analysis}
% \textbf{This is all about analysis of the simulation}
% Extensive explanation for the checklist questions can be found in Section~\ref{sec:step4}.
% \begin{itemize}
% \item Are my simulations converged enough?
% \item Am I using the right analysis techniques?
% \end{itemize}
% \end{checklist}

% \end{Checklists*}

%Checklist:
\clearpage
%%%%%%%%%%%%%%%% 
%% Checklist-specific precommands:

\newenvironment{checklist_font}{\fontfamily{lmss}\small\selectfont}{\par}
\newlist{todolist}{itemize}{2}
\setlist[todolist]{label=$\square$}
%% start checklist:
\begin{checklist_font}
\begin{itemize}
\begin{todolist}
\onecolumn
\centering
%%%%%%%%%%%%%%%%%
%%%%%% step 0
\begin{tcolorbox}[width=15cm, center]
    {\large {\color{teal}STEP 0: KNOW WHAT YOU WANT TO SIMULATE}} \newline
    \textbf{Initial questions you should ask before you set up an alchemical free energy calculation using molecular dynamics simulations}
    \item Do I understand the biology, chemistry and physics of my system?
    \item Have I properly prepared my protein and ligand systems?
    \item Does my system contain any structures that require custom parameters?
    \item What simulation protocol will provide the most evidence to answer my hypothesis?
    \item Are the projected computational expense and runtime realistic for my goals?
    \item Will my protocol be reproducible? 
    \item Will my statistics be reliable? If not, would more replicates solve the problem? Three replicates is the minimal number of replicates that should be run
    \item Can I open-source my data?
\end{tcolorbox}

%%%%%% step 1
\begin{tcolorbox}[width=15cm, center]
    {\large {\color{teal}STEP 1: PREPARING YOUR SIMULATIONS}} \newline
    \textbf{Steps to getting started setting up your alchemical free energy calculation}
    \item Make sure you know why you have picked your (combination of) force field(s)
    \item Minimize your system
    \item Equilibrate your system with your choice of thermodynamic ensemble
    \item Check the stability of your system and whether it behaves the way you want it to
\end{tcolorbox}

%%%%%% step 2
\begin{tcbraster}[raster columns=2,raster equal height, raster width=18cm]
\begin{adjustwidth}{-1cm}{}           % workaround to make the dual box pass the margin
\begin{todolist}
    \begin{tcolorbox}
    % absolute
        {\large {\color{teal}STEP 2: RUNNING ABSOLUTE SIMULATIONS}} \newline
        \textbf{Steps to running your absolute alchemical free energy calculations}

        \item Your ligands should have the same, biologically correct binding pose
        \item Make sure your \textlambda-scheduling is set correctly
        \item Check if your ligands are discharging and vanishing correctly
        \item Set up your restraints correctly
        \item Make sure you subsample in your MBAR protocol
        \item Apply the right correction terms
    \end{tcolorbox}
    \begin{tcolorbox}
    % relative
        {\large {\color{teal}STEP 2: RUNNING RELATIVE SIMULATIONS}} \newline
        \textbf{Steps to running your relative alchemical free energy calculations}
        \item           % circumvents bug in tcbraster/todolist
        \item Your ligands should have the same, biologically correct binding pose
        \item Make sure your λ-scheduling is set correctly
        \item Make sure your molecular transformations are realistic (1-5 heavy atoms for reliable computations)
        \item Generate a perturbation network by your method of choice; check whether you have enough cycle closures (preferably, every ligand should be in a cycle)
        \item Check whether dummy atoms were assigned correctly
        \item Make sure you subsample in your MBAR protocol
    \end{tcolorbox}

\end{todolist}
\end{adjustwidth}
\end{tcbraster}

%%%%%% step 3
\begin{tcolorbox}[width=15cm, center]
    {\large {\color{teal}STEP 3: HOW DO I KNOW WHICH SIMULATIONS ARE NOT RELIABLE?}} \newline
    \textbf{Situations suggesting your relative alchemical free energy calculations have not run properly (assuming absence of experimental affinities)}
    \item Standard error (\textsigma) should be \textless1 kcal·mol-1 
    \item Simulated systems have not converged 
    \newline\newline\textit{Relative:}
    \item If you observe hysteresis in perturbations and incorrect cycle closures
    \item Energy differences \textgreater15 kcal·mol-1  are unreliable
    \newline\newline\textit{Absolute:}
    \item Energies below -15 kcal·mol-1  are unreliable
    \item The ligand has not sampled most of the intended region after the vanishing step
    \item The ligand is drifting out of the intended region after the vanishing step
\end{tcolorbox}

%%%%%% step 4
\begin{tcolorbox}[width=15cm, center]
    {\large {\color{teal}STEP 4: HOW DO I KNOW WHICH SIMULATIONS ARE NOT RELIABLE?}} \newline
    \textbf{Situations suggesting your relative alchemical free energy calculations have not run properly (assuming absence of experimental affinities)}
    \item Standard error (\textsigma) should be \textless1 kcal·mol-1 
    \item Simulated systems have not converged 
    \newline\newline\textit{Relative:}
    \item If you observe hysteresis in perturbations and incorrect cycle closures
    \item Energy differences \textgreater15 kcal·mol-1  are unreliable
    \newline\newline\textit{Absolute:}
    \item Energies below -15 kcal·mol-1  are unreliable
    \item The ligand has not sampled most of the intended region after the vanishing step
    \item The ligand is drifting out of the intended region after the vanishing step
\end{tcolorbox}

%%%%%% step 5
\begin{tcolorbox}[width=15cm, center]
    {\large {\color{teal}STEP 5: WHY ARE THEY NOT RELIABLE?}} \newline
    \textbf{Suggestions for finding out why your alchemical free energy calculations may not be reliable}
    \item Check again whether dummy atoms were assigned correctly
    \item Inspect the trajectories across the λ-schedule (particularly the endpoints)
    \item Inspect the overlap matrices
\end{tcolorbox}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% IMPORTANT USER CONFIGURATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[most]{tcolorbox}
\newcommand{\versionnumber}{0.1}  % you should update the minor version number in preprints and major version number of submissions.
\newcommand{\githubrepository}{\url{https://github.com/michellab/alchemical-best-practices}}  %this should be the main github repository for this article
\newcommand{\expect}[1]{\left\langle{#1}\right\rangle}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% ARTICLE SETUP
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Best Practices for Alchemical Free Energy Calculations: v\versionnumber}
\author[7]{Bryce K. Allen}
\author[1*]{John D. Chodera}
\author[2,12]{Maximilian Kuhn}
\author[2*]{Antonia S. J. S. Mey}
\author[2*]{Julien Michel}
\author[3*]{David L. Mobley}
\author[1]{Levi N. Naden}
\author[4]{Samarjeet Prasad}
\author[5]{Julia E. Rice}
\author[1,9]{Andrea Rizzi}
\author[2]{Jenke Scheen}
\author[6*]{Michael Shirts}
\author[11]{Gary Tresadern}
\author[10]{Huafeng Xu}

@@

\begin{figure}
    \includegraphics[width=0.95\linewidth]{figures/fig1_what_is_alchemy/Fig1.pdf}    \caption{Illustration of the types of free energies differences that can be calculated using alchemical free energy methods. A: Change in free energy due to a conformational change. B: Partition coefficient such as $\log P$ or $\log D$, here as an example the partition coefficient between methanol and water of a given molecule. C: Free energies of membrane insertions. D: Simulations of protein or other host molecule simulations. E: Absolute free energies of binding of a small molecule to a host (e.g. protein), F: Relative free energy of binding of one molecule with respect to another, here toluene and benzyl alcohol.
    \label{fig:fig1_what_is_alchemy}
    }
\end{figure}

@@

    \includegraphics[width=0.95\linewidth]{figures/fig2_what_is_lam/Fig2.pdf}

@@

\begin{figure}
    \includegraphics[width=0.95\linewidth]{figures/fig3_therm_cyc/Fig3.pdf}
    \caption{{\bf Thermodynamic cycle for computing the relative free energy of binding ($\Delta \Delta G$) between two related small molecules to a supramolecular host.}
    The relative binding free energy difference between two small molecules, $\Delta \Delta G_{\mathrm{bind}, A \rightarrow B} \equiv \Delta G_{\mathrm{bind}, B} - \Delta G_{\mathrm{bind}, A}$---here benzyl alcohol (top) to toluene (bottom)---can be computed as a difference between two alchemical transformations, $\Delta G_\mathrm{bound} - \Delta G_\mathrm{solvated}$, where $\Delta G_\mathrm{bound}$ represents the free energy change of transforming $A \rightarrow B$ in complex and $\Delta G_\mathrm{solvated}$ the free energy change of transforming $A \rightarrow B$ in solvent.}
    \label{fig:fig3_binding-thermodynamic-cycle}
\end{figure}
\todo[inline, color=green!20]{This section needs to be expanded and give a good introduction to the theoretical background without going into too much detail.}

@@

Running binding FE calculations in a drug discovery application will typically require the use of software or tools to facilitate the calculations of many compounds. The commercial implementation from Schrodinger, FEP+, uses a graphical user interface and once the user has calculated any missing force field parameters, calculations can be prepared and submitted within minutes. The software builds the network of perturbations, connecting similar compounds based on LOMAP methodology~\cite{liu2013lead}, all inputs for the Desmond simulations are built automatically and the job can be saved or run immediately on available GPUs. The cost of this software is often prohibitive but alternative tools are becoming available to allow relatively straight forward running of alchemical FE calculations with other software~\cite{2015pmx, loeffler2015fesetup} (CITE New Merz paper, cite PMX paper Vytas and Bert de Groot, cite FESETUP, cite FEanalysis). One consideration at this point is to define the perturbations suitable for the application. For instance, if the goal is to accurately assess the relative binding energy of a small number of compounds, possibly with challenging synthesis, the map of perturbations may contain as many connections between compounds as affordable. However, when running calculations on hundreds of compounds a so called ‘star-map’ can be used that just contains one connection per compound: perturbing every compound to a central ligand, typically the crystal structure ligand. In this way the top-ranking examples can be readily identified and submitted to additional calculations in a second round. 

@@

\paragraph{Topologies} A critical first step in relative calculations is to select an approach to these calculations, determining whether to use a \emph{dual topology}, \emph{single topology}, or \emph{hybrid topology} approach to relative calculations.
\begin{figure}
    \includegraphics[width=0.95\columnwidth]{figures/fig4_topol/Fig4.pdf}
    \caption{top: single topology bottom: dual topology Figure adapted from \url{http://www.alchemistry.org/wiki/Constructing_a_Pathway_of_Intermediate_States}}
    \label{fig:fig4_topology}
\end{figure} 
The distinction between these can be illustrated by considering a hypothetical transformation from molecule A to molecule B, where both atoms share a common substructure but differ in which functional groups are present; e.g. consider a transformation of benzene (A) to benzyl alcohol (B)~\ref{fig:fig4_topology}.
In this case the common substructure is the benzene ring, though perhaps may be larger depending on how it is defined, as we discuss below.
In single topology calculations, the overall transformation is set up to involve as few additional atoms as possible, so benzene would be typically changed into benzyl alcohol by changing one of the hydrogens into a carbon. To this new carbon you also find non-interacting atoms called ``dummy atoms'' (retaining their bonded interactions but not interacting with the rest of the system), which will become the two hydrogens attached to the new carbon and the OH group. Bond parameters as well as partial charges are adjusted accordingly. 
Thus in a single topology calculation, atoms may change their type so relatively few dummy atoms are created. This is illustrated in fig.~\ref{fig:fig4_topology} (a). 
In contrast, in a dual topology free energy calculation, no atoms are allowed to change type~\cite{shirts2012best}. This means that the benzene to benzyl alcohol transformation involves starting with benzene plus the non-interacting dummy atoms making up the hydroxy methyl group, then passing through an intermediate state where atoms which are becoming dummy atoms or ceasing being dummy atoms are partially interacting (this state may or may not be well defined~\cite{mobley2014blind}  and culminating in a state where benzyl alcohol is present along with the additional dummy atoms which was previously a corresponding hydrogen of the benzene. Fig.~\ref{fig:fig4_topology} (b) depicts how such a dual topology works.

@@

\paragraph{Atom mapping}
Once a particular approach to the topology is selected, a crucial next step is to identify the common atoms which will not be perturbed.
Rigorously, this process essentially comprises a maximal common substructure (MCSS) search of the molecules involved to identify the common substructure -- though the parameters of the MCSS search will differ depending on whether single or dual topology calculations are planned.
Specifically, with a single topology approach in mind, atom types are allowed to change, so a permissive MCSS search can be done, whereas with dual topology a more strict search is required.
\begin{figure}
    \includegraphics[width=0.95\linewidth]{figures/fig5_mcs/MCS.pdf}
    \caption{A: restrictive MCSS match B: ring breaking}
    \label{fig:fig5_mcss}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=0.95\linewidth]{figures/fig6_thermo_cyc_abs/fig6_therm_abs.pdf}
    \caption{Absolute thermodynamic cycle}
    \label{fig:fig6_absolute-thermodynamic-cycle}
\end{figure}

@@

\ref{fig:fig7_ampling_scheme} A:\cite{hedges2019biosimspace, song2019using } B\cite{aldeghi2015accurate, wang2015accurate,jiang2019computing} C:\cite{li2007simulated, tan2017optimally} D:\cite{aldeghi2018accurate}
\begin{figure}
    \includegraphics[width=0.95\columnwidth]{figures/fig7_sampl_scheme/sampling_schemes.pdf}
    \caption{\textbf{There are 4 different sampling strategies available and implementations are available for different software packages.} A: Multiple replicas in parallel at different lambda states. B: Hamiltonian replica exchange scheme. C: Single replica scheme sampling from all $\lambda$ states. D: Non-equilibrium sampling scheme.}
    \label{fig:fig7_sampling_scheme}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.95\linewidth]{figures/fig9_forward_reverse/Forward_Reverse_Fig.pdf}
    \caption{Free energy (in k$_{B}$T) for two different relative binding free energy (RBFE) perturbations. 
    Each plot shows the estimated free energy change using a varying fraction of total simulation time (up to 5 ns total). 
    The top panel shows the three-step protocol for a perturbation involving 5 perturbed atoms, while the bottom panel shows the same protocol for a perturbation involving 10 perturbed atoms. The difference in energy between the forward (blue) and reverse (red) free energy calculations at the midpoint of the simulation time gives an indication of the overall convergence of the simulation, with differences over 1 k$_{B}$T indicating poor convergence.}
    \label{fig:convergence_forward_reverse}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.95\linewidth]{figures/fig10_equib_detection/fig10_equib.pdf}
    \caption{{\bf Automatic partitioning into equilibration and production regions.}
    \emph{Top:} The average (black line) standard deviation (shaded region) of the reduced potential $u^*$ over many independent replicate simulations started from the same initial conditions show a significant initial transient before relaxing to the true average potential energy.
    \emph{Middle:} A cumulative average (red) of the entire simulation data demonstrates a bias in the estimate of the average potential $<u>$ that persists far beyond the initial transient relaxation time, while averaging a production region that omits the initial transient (blue) eliminates this bias.
    \emph{Bottom:} A simple automated approach to determination of the equilibration boundary $t_0$ suggested in~\cite{chodera2016simple} examines the number of effectively uncorrelated samples $N_{\mathrm{eff}_{[t_0,T]}} = (T-t_0) / g_{[t_0,T]}$ within the proposed production region $[t_0,T]$ by computing the statistical inefficiency $g_{[t_0,T]}$ for that simulation interval.
    $N_{\mathrm{eff}_{[t_0,T]}}$ has the general behavior of increasing linearly as $t_0$ moves backwards from $T$ until the initial transient relaxation is encountered, at which point it plunges.
    The optimal equilibration boundary $t_0$ is selected to maximize the number of uncorrelated samples.
    \emph{Figure adapted from~\cite{chodera2016simple}.}
    \todo[inline]{JDC will update this figure with something similar for a real alchemical free energy calculation.}
    }
    \label{fig:automatic-equilibration-detection}
\end{figure}

@@

\includegraphics[width=0.95\columnwidth]{figures/fig11_overlap/overlap_matrices.pdf}

@@

\todo[inline, color={green!20}]{ASJSM: Please upload the correct figure here and modify the path below}
\begin{figure}
    \includegraphics[width=0.95\linewidth]{figures/fig8_convergence/free_energy_trajectories.pdf}
    \caption{Average binding free energy of 5 replicate Hamiltonian replica exchange calculations as a function of total simulation time (i.e. the sum of the simulation time of all replicas) for the two host-guest systems CB8-G3 and OA-G3. Shaded areas represent 95\% confidence intervals around the mean computed from the 5 replicates data. The horizontal dashed lines show the final binding free energy prediction of the two calculations after a total of ~5230 ns for OA-G3 and ~6650 ns for CB8-G3. Longer correlation times in CB8-G3 cause the calculation to converge more slowly. The original data used to generate the plot can be found at \url{https://github.com/MobleyLab/SAMPL6/blob/master/host_guest/Analysis/SAMPLing/Data/reference_free_energies.csv}.
}
    \label{fig:freeenergytrajectories}
\end{figure}

@@

\section{Checklist}
\label{sec:checklist}
\todo[inline, color={green!20}]{ASJSM: @Volunteer This needs to be revised and expanded, some initial thoughts were just thrown in.}
An attempt at identifying most important checklist items.

% This provides a checklist which
% - spans a full page
% - consists of multiple sub-checklists
% - exists on a separate page
% This style of checklist will be especially helpful if you want to encourage readers to print and use your checklist in practice, as they
% can easily print it without also printing other material from your manuscript. However, other styles of checklist are also possible (below).
\begin{Checklists*}[p!]

\begin{checklist}{Step 0 -- Know what you want to simulate }
\textbf{What are the first questions that need addressing before setting up a molecular dynamics simulation}\\
Extensive explanation for the checklist questions can be found in Section~\ref{sec:step0}.
\begin{itemize}
\item Can I get the required accuracy with the simulation I want to carry out?
\item Have I properly prepared my protein and ligand systems?
\item Does my system contain any groups that require custom parameters?
\item What simulation protocol will provide the most evidence to answer my hypothesis?

\item And finally
\end{itemize}
\end{checklist}

\begin{checklist}{Simulation preparation}
\textbf{How do I get started setting up an alchemical free energy calculation}
Extensive explanation for the checklist questions can be found in Section~\ref{sec:step1}.
\begin{itemize}
\item Have I followed the Best practices for biomolecular simulation set up?
\item In a relative simulation, will I run into problems with clashing geometries in the ligand transformation or crystal waters?
\end{itemize}
\end{checklist}
\end{Checklists*}

\begin{Checklists*}[p!]
\begin{checklist}{Absolute simulations}
\textbf{What are the main things I need to consider for an absolute alchemical free energy calculation?}
Extensive explanation for the checklist questions can be found in Section~\ref{sec:step2}.
\begin{itemize}
\item Topology
\item Restraints
\item Standard state handling
\end{itemize}
\end{checklist}

\begin{checklist}{Relative simulations}
\textbf{What are the main things I need to consider for an relative alchemical free energy calculation?}
Extensive explanation for the checklist questions can be found in Section~\ref{sec:step2}.
\begin{itemize}
\item First thing
\item Also remember
\item And finally
\end{itemize}
\end{checklist}

\begin{checklist}{Analysis}
\textbf{This is all about analysis of the simulation}
Extensive explanation for the checklist questions can be found in Section~\ref{sec:step4}.
\begin{itemize}
\item Are my simulations converged enough?
\item Am I using the right analysis techniques?
\end{itemize}
\end{checklist}

\end{Checklists*}
\clearpage

\section*{Author Contributions}
%%%%%%%%%%%%%%%%
% This section mustt describe the actual contributions of
% author. Since this is an electronic-only journal, there is
% no length limit when you describe the authors' contributions,
% so we recommend describing what they actually did rather than
% simply categorizing them in a small number of
% predefined roles as might be done in other journals.
%
% See the policies ``Policies on Authorship'' section of https://livecoms.github.io
% for more information on deciding on authorship and author order.
%%%%%%%%%%%%%%%%
\todo[inline, color={green!20}]{ASJSM: @everyone, can you check your contribution is acknowledge and if not add the appropriate information. }
(Explain the contributions of the different authors here)
ASJSM: Coordinated the document, contributed to most sections, and created figures \ref{fig:fig2_what_is_lambda},~\ref{fig:fig7_sampling_scheme},~\ref{fig:overlap} and replotted~\ref{fig:automatic-equilibration-detection} 
\textit{JS}: created figures \ref{fig:fig1_what_is_alchemy}, \ref{fig:fig3_binding-thermodynamic-cycle}-\ref{fig:fig6_absolute-thermodynamic-cycle} and contributed to general formatting discussions. 
% We suggest you preserve this comment:
For a more detailed description of author contributions,
see the GitHub issue tracking and changelog at \githubrepository.
